---
title: "heart disease (exploratory data analysis)"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(shiny)
library(dplyr)
library(ggplot2)
```

```{r}
df <- read.csv("D:/R files/R_file/heart EDA/heart.csv")
```

# Page 1

## Row

### VALUE BOX

```{r}
count<-count(df , target)
valueBox(526, caption = "healthy people" , icon = "fa-user")
```

### value box 2

```{r}
valueBox(499, caption = "sick people" , icon = "fa-user")
```

### value box 3

```{r}
valueBox(713, caption = "no. of male " , icon = "fa-user")
```

### value box 4

```{r}
valueBox(312, caption = "no. of female" , icon = "fa-user")
```

## Column

### percentage of sick and healthy

```{r}
renderPlotly({
   count<-count(df , target)
fig<-plot_ly(count,labels=c("sick","healthy") ,values=count$n , type = "pie" ,marker = list(colors=c("#265094","#cc4343")))
fig<-fig%>%layout(title="percentage of sick and healthy")
fig
})
```

### percentage of men and woman

```{r}
renderPlotly({
   count_1<-count(df,sex)
fig_1<-plot_ly(count_1,labels=c("female","male") ,values=count_1$n , type = "pie" , marker = list(colors=c("#265094","#cc4343")))
fig_1<-fig_1%>%layout(title="percentage of man and woman")
fig_1
})
```

### percentage of type of chest pain

```{r}
cout_2<-count(df , cp)
renderPlotly({
fig_2<-plot_ly(cout_2,labels=c("0","1" , "2" , "3") ,values=cout_2$n , type = "pie" , marker = list(colors=c("#265094","#cc4343")))
fig_2<-fig_2%>%layout(title="type of cheat pain")
fig_2})
```

# Page 2

## Row

### value box1

```{r}
valueBox(max(cout_2$n) , caption="maximum no of chast pain of type 0" , icon = "fa-user")
```

### value box2

```{r}
valueBox(max(df$age), caption="oldest person" , icon = "fa-user")
```

### value box 3

```{r}
valueBox(max(df$trestbps), caption="highest blood pressure" , icon = "fa-user")
```

### value box 3

```{r}
valueBox(max(df$chol), caption="highset cholestroal" , icon = "fa-user")
```

## Row

### types of chest pain

```{r}
renderPlot(
   
ggplot(df,aes(x = cp)) + 
   geom_bar(position = position_dodge(preserve = "single"),fill="#7a0f34")
)
```

### age of patients

```{r}
renderPlot(
   hist(df$age , col = "#3c4d82" ,xlab = "age" , ylab="" , main="age of patients",breaks=100)

)
```

### resting blood pressure

```{r}
renderPlot(
   hist(df$trestbps , col = "#3c4d82" ,xlab = "blood pressure" , ylab="" , main="resting blood pressure",breaks=100)
)
```

### cholesterol in blood

```{r}
renderPlot(
hist(df$chol , col = "#3c4d82" ,xlab = "cholestroal" , ylab="" , main="choletrol in blood" , breaks = 20)

)
```

# Page 3

## Row

### scatter plot for blood pressure

```{r}
renderPlot(
ggplot(df,aes(x=thalach , y=trestbps))+geom_point()+geom_density_2d()
)
```

### scatter plot of cholesterol and blood pressure

```{r}
renderPlot(
ggplot(df,aes(x=chol , y=trestbps))+geom_point()+geom_density_2d()
)
```
